Bayesian Neural Networks

### 2024-03-25 Paper/paper.tex
Updated paper

\subsection{Neural Networks}

Convolutional neural networks are a type of neural network that is better suited for

\subsection{Bayesian Neural Networks}

Bayesian Neural were invented by Ralph Merkle. Ralph Merkle initially patented Merkle trees for digital signatures....

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
	\caption{Basic Merkle Tree\cite{wikipedia-merkle-tree}}
\end{figure}

....

@@

\section{Literature Review}

\section{How it works}

\section{Use Cases}

...

@@

We use a bayesian convolutional neural network implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}

>>>>

@@

\section{Neural Network}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		% Define node styles
		\tikzstyle{neuron} = [circle, draw, minimum size=1.5cm];
		\tikzstyle{weight} = [font=\scriptsize];

		% Input layer (2 neurons)
		\node[neuron] (input1) at (-2,1) {Input 1};
		\node[neuron] (input2) at (-2,-1) {Input 2};

		% Hidden layer (3 neurons)
		\node[neuron] (hidden1) at (2,2) {Hidden 1};
		\node[neuron] (hidden2) at (2,0) {Hidden 2};
		\node[neuron] (hidden3) at (2,-2) {Hidden 3};

		% Output layer (2 neurons for classification)
		\node[neuron] (output1) at (6,1) {Class 1};
		\node[neuron] (output2) at (6,-1) {Class 2};

		% Connections with weights
		\draw[->] (input1) -- node[weight, above] {$w_{1,1}$} (hidden1);
		\draw[->] (input2) -- node[weight, above] {$w_{2,1}$} (hidden1);
		\draw[->] (input1) -- node[weight, right] {$w_{1,2}$} (hidden2);
		\draw[->] (input2) -- node[weight, right] {$w_{2,2}$} (hidden2);
		\draw[->] (input1) -- node[weight, above] {$w_{1,3}$} (hidden3);
		\draw[->] (input2) -- node[weight, above] {$w_{2,3}$} (hidden3);
		\draw[->] (hidden1) -- node[weight, right] {$v_{1,1}$} (output1);
		\draw[->] (hidden2) -- node[weight, right] {$v_{2,1}$} (output1);
		\draw[->] (hidden3) -- node[weight, right] {$v_{3,1}$} (output1);
		\draw[->] (hidden1) -- node[weight, above] {$v_{12}$} (output2);
		\draw[->] (hidden2) -- node[weight, above] {$v_{2,2}$} (output2);
		\draw[->] (hidden3) -- node[weight, above] {$v_{3,2}$} (output2);
	\end{tikzpicture}
	\caption{Example neural network}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/big-pic-cnn.jpg}
	\caption{CNN pipeline \cite{eli5CNN}}
\end{figure}

Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition. Instead of reading the entire image a CNN slides over the image...

The result is that the neural network trains faster..

\section{Bayesian Neural Networks}

Bayesian neural networks take the

\subsection{Bayesian Conolutional Neural Networks}

Same principle...

@@

We use a BCNN implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}

\subsection{CIFAR-10}

	\begin{figure}H
		\centering
	\includegraphics[width=.75\textwidth]{../Images/cifar-10.png}
	\caption{Example CIFAR-10 images \cite{cifar10}}
\end{figure}

The CIFAR-10 dataset...

\subsection{Hyperparamaters}

We used the following hyperparamaters for training
	\begin{center}
		\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
			\hline
			\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
			\hline\hline
			Epochs & 500 & 500\\
			\hline
			Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
			\hline
			Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
			\hline
			Optimizer & Adamw  & Adamw  \\
			\hline
		\end{tabular}
	\end{center}

\subsection{Results}
